---
title: "Homework Data Visualization"
author: "Kittipong Hor"
date: "2023-03-31"
output:
  pdf_document: default
  html_document: default
---

# Hello World

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
data("diamonds")
```

### Chart 1 - A Histogram of the price of all the diamonds in the diamond data set
```{r message=FALSE, warning=FALSE}
ggplot(diamonds, aes(price)) +
  geom_histogram(bins=20, 
                 col="black",
                 fill = "salmon") +
  theme_minimal() +
  labs(title = "Diamond Prices")
summary(diamonds$price)
```

We found a positive skewness in this histogram chart

### Chart 2 - A Scatterplot of diamond price vs. carat
```{r message=FALSE, warning=FALSE}
set.seed(18)
ggplot(diamonds %>% sample_n(5000), aes(carat,price, col=cut))+
  geom_point() +
  geom_smooth(method = "lm",
              col = "red") +
  labs(title = "Diamond prices by Carat")
```

We found a positive correlation between two variables.

### Chart 3 - A Boxplot of sample diamond price vs. color
```{r message=FALSE, warning=FALSE}
set.seed(18)
ggplot(diamonds %>% sample_n(5000), aes(color,price)) +
  geom_boxplot(fill= "gold") +
  theme_minimal() +
  labs(title = "Diamond prices by color")
```

We found a result summaries of diamond colors.

### Chart 4 A Barplot of diamond cut by color.
```{r message=FALSE, warning=FALSE}
set.seed(18)
ggplot(diamonds %>% sample_n(5000), aes(cut, fill=color)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  labs(title = "Diamond Cut")
```

We found a proportion of color diamonds for each value of cut

### Chart 5 A Scatterplot of diamond price vs. carat
```{r message=FALSE, warning=FALSE}
set.seed(18)
ggplot(diamonds %>% sample_n(5000), aes(carat,price)) +
         geom_point() +
         geom_smooth(method ="lm",col="red") +
         facet_wrap(~clarity, ncol = 2) +
         theme_minimal() +
         labs(title = "diamond prices by carat")
```

We found a positive correlation between two variables by clarity.
